\Large {\bf rt1d: Documentation}

### 2012-05-07 doc/manual/rt1d_manual.tex
Started implementing MCD+PL SED.  Need to think more about time-dependent SEDs.  Pausing to dotdictify pfs in major classes.

At each time-step, we also solve for the temperature evolution, $dT_k/dt$,
which
is given by
\begin{align}
    \frac{3}{2}\frac{d}{dt}\left(\frac{\kB T_k \ntot}{\mu}\right) & = \fheat  \sum_i n_i \Heat_i - \sum_i \zeta_i n_e n_i - \sum_i \eta_i n_e n_i \nonumber \\ & - \sum_i \psi_i n_e n_i - \omega_{\HeII} n_e \nHeII \label{eq:TemperatureEvolution} 
\end{align}
where $\Heat_i$ is the photo-electric heating rate coefficient (due to
electrons previously bound to species $i$), $\omega_{\HeII}$ is the dielectric
recombination cooling coefficient, and $\zeta_i$, $\eta_i$, and $\psi_i$ are
the collisional ionization, recombination, and collisional excitation cooling
coefficients, respectively. The constants in Equation
\ref{eq:TemperatureEvolution} are the total number density of baryons, $\ntot
= n_\mathrm{H} + n_{\mathrm{He}} + n_e$, the mean molecular weight, $\mu$,
Boltzmann's constant, $\kB$, and the fraction of secondary electron energy
deposited as heat, $\fheat$. We use the formulae in Appendix B of
\citet{Fukugita1994} to compute the values of $\alpha_i$, $\beta_i$, $\xi_i$,
$\zeta_i$, $\eta_i$, $\psi_i$, and $\omega_{\HeII}$.

@@

% Secondary Electrons
\subsection{Additional Complexity: Energy Dependent Secondary Electron Treatment}
In the previous section (and in all of Mirocha et al. 2012), we considered the asymptotic limit of \citet{Shull1985}, in which the fractional energy deposition of secondary electrons as heat, ionization, and excitation depends only on the hydrogen ionized fraction.  \citet{Furlanetto2010} updated this work, providing lookup tables of deposition fraction as a function of both ionized fraction and electron energy.  These effects are most important at $E \lesssim 10^2$ eV.

@@

\item [\texttt{ProblemType = 2.2}] Same as \texttt{ProblemType = 2}, except we sample the continuous blackbody spectrum with the four energy groups used by Mirocha et al. (2012).

@@

>>>>

At each time-step, we also solve for the temperature evolution, $dT_k/dt$,
which
is given by
\begin{align}
    \frac{3}{2}\frac{d}{dt}\left(\frac{\kB T_k \ntot}{\mu}\right) & = \fheat  \sum_i n_i \Heat_i - \sum_i \zeta_i n_e n_i - \sum_{i^{\prime}} \eta_i n_e n_i \nonumber \\ & - \sum_i \psi_i n_e n_i - \omega_{\HeII} n_e \nHeII \label{eq:TemperatureEvolution} 
\end{align}
where the index $i$ corresponds as usual to species that have bound electrons,
and $i^{\prime}$ corresponds to ionized species. $\Heat_i$ is the
photo-electric heating rate coefficient (due to electrons previously bound to
species $i$), $\omega_{\HeII}$ is the dielectric recombination cooling
coefficient, and $\zeta_i$, $\eta_i$, and $\psi_i$ are the collisional
ionization, recombination, and collisional excitation cooling coefficients,
respectively. The constants in Equation \ref{eq:TemperatureEvolution} are the
total number density of baryons, $\ntot = n_\mathrm{H} + n_{\mathrm{He}} +
n_e$, the mean molecular weight, $\mu$, Boltzmann's constant, $\kB$, and the
fraction of secondary electron energy deposited as heat, $\fheat$. We use the
formulae in Appendix B of \citet{Fukugita1994} to compute the values of
$\alpha_i$, $\beta_i$, $\xi_i$, $\zeta_i$, $\eta_i$, $\psi_i$, and
$\omega_{\HeII}$.

@@

% Secondary Electrons
\subsection{Additional Complexity: Energy Dependent Secondary Electron Treatment}
In the previous section (and in all of \citet{Mirocha2012}), we considered the asymptotic limit of \citet{Shull1985}, in which the fractional energy deposition of secondary electrons as heat, ionization, and excitation depends only on the hydrogen ionized fraction.  \citet{Furlanetto2010} updated this work, providing lookup tables of deposition fraction as a function of both ionized fraction and electron energy.  These effects are most important at $E \lesssim 10^2$ eV.

@@

\item [\texttt{ProblemType = 2.2}] Same as \texttt{ProblemType = 2}, except we sample the continuous blackbody spectrum with the four energy groups used by \citet{Mirocha2012}.

@@

\item \texttt{SourceType}
\begin{description}
    \item [0] Monochromatic source.
    \item [1] Blackbody.  
    \item [2] PopIII star.  
    \item [3] Power-law.        
    \item [4] Absorbed power-law (column density given by \texttt{SpectrumAbsorbingColumn} parameter).
    \item [5] Multi-color disk + power-law. Relative normalization given by \texttt{SpectrumDiskFraction} parameter.                
\end{description}
